Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2019-08-06 paper/galsize_paper.tex
Added Andrey's final suggestion for a data table of galaxy sample information.

We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds: an  $\mstar>10^{9.75}\msun$ sample with $z_{\rm max}=0.0435$ and $N_{\rm gal}=27658;$ an  $\mstar>10^{10.25}\msun$ sample with $z_{\rm max}=0.0663$ and $N_{\rm gal}=48571;$
an  $\mstar>10^{10.75}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=52350;$
and an  $\mstar>10^{11}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=33578.$ We follow standard practice \citep[e.g.,][]{zehavi_etal11} and throw out all galaxies with $z<z_{\rm min}=0.02$ to minimize lightcone effects; to minimize the effect of redshift evolution we also throw out galaxies with redshift $z \geq z_{\rm max}=0.1,$ including cases where a volume-limited sample would be attainable out to higher redshift.

>>>>

We measure $\wproj(\rproj)$ separately for large and small subsamples for four different thresholds in $\log_{10}\mstar/\msun:$ 9.75, 10.25, 10.75, and 11. We follow standard practice \citep[e.g.,][]{zehavi_etal11} and throw out all galaxies with $z<z_{\rm min}=0.02$ to minimize lightcone effects; to minimize the effect of redshift evolution we also throw out galaxies with redshift $z \geq z_{\rm max}=0.1,$ including cases where a volume-limited sample would be attainable out to higher redshift. We refer to Table \ref{table:data} for a summary of our volume-limited galaxy samples.

\begin{table}
\caption{Summary of SDSS galaxy samples used as constraining data. The stellar mass threshold defining the mass-limited sample appears in the leftmost column. The remaining columns show the redshift range and the total number of galaxies in each sample. } % title of Table
\centering % used for centering table
\begin{tabular}{c c c c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
$\log_{10}\mstar^{\rm min}/M_{\odot}$ & $z_{\rm min}$ & $z_{\rm max}$ & $N_{\rm gal}$ \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
9.75 & 0.02 & 0.0435 & 27658 \\ % inserting body of the table
10.25 & 0.02 & 0.0663 & 48571\\
10.75 & 0.02 & 0.1 & 52350 \\
11 & 0.02 & 0.1 & 33578 \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
\label{table:data} % is used to refer this table in the text
\end{table}
